---
title: "**Machine learning models**"
subtitle: "**REPORT**"
author: "Roberto J. Alcaraz Molina"
output: pdf_document
params:
  data_part: 0.75
  control: "cv"
  model: "knn"
---
```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      echo = F, 
                      message = FALSE,
                      fig.pos="H", 
                      fig.align="center",
                      fig.width=10,
                      cache=FALSE, error = F,
                      class.output = "bg-primary")
```

<style>
div.blue pre { background-color:lightblue; }
div.blue pre.r { background-color:blue; }
</style>

```{r}
pacman::p_load(shiny, tidyverse, ggplot2, magrittr, gapminder, plotly, shinythemes, shinyjs, DT, leaflet, knitr,Stat2Data, dplyr, patchwork, ggpubr, htmlwidgets, shinythemes, GGally, ggforce, maps, network, viridis, devtools, kaggler, caret, reticulate, mice, readr)
```

```{r, echo=F}
vehicles <- readr::read_csv("https://raw.githubusercontent.com/RoberAlcaraz/First-Take-Away/main/vehicles_data.csv")

vehicles[sapply(vehicles, is.character)] <- lapply(vehicles[sapply(vehicles, is.character)], 
                                                     as.factor)
vehicles$state <- as.character(vehicles$state)

model.fitting <- function(partition, control, model){
  
  set.seed(0)
  training <- createDataPartition(vehicles$price, p = partition, list = F)
  vehiclesTrain <- vehicles[training, ]
  vehiclesTest <- vehicles[-training, ]
  
  ctrl <- trainControl(method = control,
                       number = 5, classProbs = T, verboseIter = F)
  
  form <- as.formula(price ~ year + odometer + manufacturer + condition + fuel + title_status + transmission + drive)
  fit.mod <- train(form, 
                   method = model,
                   data = as.data.frame(vehiclesTrain),
                   metric = "Accuracy",
                   trControl = ctrl,
                   preProcess = c("BoxCox", "center", "scale"))
  
  pred <- predict(fit.mod, vehiclesTest)
  CM <- confusionMatrix(pred, vehiclesTest$price)
  
  invisible(list(fit = fit.mod, confMatrix = CM))
}
```


Here, there are your results of the model:

  - First of all, we can select the percentage of the data set that is employed 
  to train the model. You have selected a `r 100*params$data_part` %.
  
  - Then, we can choose the method of resampling between cross validation or boostrap. 
  You have selected `r params$control`.
  
  - Finally, we can select between five different models, taking into account that
  some of them needs some time to train. You have selected the model `r params$model`.
  
## Summary of the model

```{r, echo=F}
fit.mod <- model.fitting(params$data_part, params$control, params$model)
```

<div class = "blue">
```{r, echo=F}
fit.mod$fit
```
</div>


## Confusion Matrix

<div class = "blue">
```{r, echo=F}
fit.mod$confMatrix
```
</div>


## Variable Importance

<div class = "blue">
```{r, echo=F}
plot_imp <- varImp(fit.mod$fit, scale = T)
plot(plot_imp, scales = list(y = list(cex = .95)), top = 5)
```
</div>
